Natural Stories LM analysis

### 2020-08-26 Analysis/nat_stories_lms.Rmd
add analysis of all data

@@

@@

>>>>

This is all data from participants who speak English that wasn't a mistake. (So, includes bad participants and post-mistake data.)

@@

summary(no_surp)
summary(ngram_only)
summary(grnn_only)
summary(txl_only)

@@

BRM models from this same very permissive data. 
```{r brm-models}

any_grnn <- read_rds("brm_grnn_any_center.rds")
any_txl <- read_rds("brm_txl_any_center.rds")
any_ngram <- read_rds("brm_ngram_any_center.rds")

summary(any_grnn)
summary(any_txl)
summary(any_ngram)

  stats
}
a <- show_summary(any_txl) %>% mutate(model="TXL") %>% mutate(Term=str_replace(Term,"txl","surp"))
b <- show_summary(any_grnn) %>% mutate(model="GRNN") %>% mutate(Term=str_replace(Term,"grnn","surp"))
c <- show_summary(any_ngram) %>% mutate(model="5-gram") %>% mutate(Term=str_replace(Term,"ngram","surp"))
